Efficient static analysis of Marlowe contracts

### 2020-05-04 papers/static_analysis2020/paper.tex
Fix typo

We have also seen that many specific properties and restrictions characteristic
of the target DSL can be utilized both as optimisation opportunities
and, in our case, for completeness of the analysis. Since symbolic
execution of, for example, a turing complete language, would be intractable,
and would require us to manually set a bound; but this is not in the
case for Marlowe.

>>>>

We have also seen that many specific properties and restrictions characteristic
of the target DSL can be utilized both as optimisation opportunities
and, in our case, for completeness of the analysis. Symbolic execution
of, for example, a turing complete language, would be intractable,
and would require us to manually set a bound; but this is not in the
case for Marlowe.
